Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of NIRCam Detectors

### 2018-08-23 ms.tex
more intro stuff.

%% Reintroduced the \received and \accepted commands from AASTeX v5.2
\received{July 1, 2016}
\revised{September 27, 2016}
\accepted{\today}
%% Command to document which AAS Journal the manuscript was submitted to.
%% Adds "Submitted to " the arguement.
\submitjournal{ApJ}

@@

\author{Douglas Kelly}
\affiliation{Steward Observatory \\
933 North Cherry Avenue \\
Tucson, AZ 85721, USA}

@@

@@

JWST transmission and emission spectra of transiting exoplanets will provide invaluable glimpses at exoplanet atmospheres that reveal the composition and temperature structure at a level never achieved before.
This promising science from JWST, however, will require exquisite precision and understanding of systematic errors that can impact the time series of planets crossing in front of and behind their host stars.
This is especially true if JWST is used to search for biosignatures in temperature atmospheres on Earth-sized planets that may contain liquid water.
Here, we provide the lessons learned from ground-based characterization of the NIRCam H2RG detectors, which will be used for exoplanet spectra and are the same type of detectors used in JWST's NIRISS and NIRSpec instruments.
We summarize the lessons learned from cryogenic vacuum campaigns 2 and 3 at NASA Goddard and NASA Johnson with the flight hardware as well as laboratory tests of the same detectors at the University of Arizona's Steward Observatory.

@@

JWST will provide powerful new measurements of exoplanet atmospheres with spectroscopy from 0.6 to 12 $\mu$m
\citep{beichman2014pasp,greene2016jwst_trans,howe2017informationJWST,barstow2015jwstSystematics,schlawin2018JWSTforecasts}
The sensitivity of JWST combined with its unprecedented wavelength coverage on exoplanets will enable it to measure the abundance of carbon-bearing molecules (CO, CO$2$ and CH$_4$) as well as study cooler, smaller planets than previously characterized.

JWST has also been considered for observations of temperate Earth-like planets that orbit their stars at a distance where where water could be in liquid form on their surface.
The TRAPPIST-1 system \citep{gillon2016trappist1Discovery,gillon2017trappist-1sevenp} presents an exciting opportunity to study Earth-sized stars orbiting a 0.1~R$_\odot$ M-type star.
By putting together 30 transits, it may be possible to collect enough photons to detect CO$_2$ and possible O$_3$ in the atmosphere of TRAPPIST-1 d with JWST \citep{barstow2016trappist1habitable} if clouds have a minimal impact to its atmosphere.
A critical question in studying a planet like TRAPPIST-1 d, however, is whether photon-limited performance is possible with JWST observations.

@@

Ground-based

The extreme precision needed to study Earth-like planets is 
Section \ref{sec:obs} describes the observations.

Known detector effects that could affect stability:
\begin{itemize}[noitemsep]
	\item Intrapixel sensitivity - including sub-pixel flat fielding issues, sub-pixel crosshatching on the detectors
	\item Asic-specific effects - pre-amp reset
\end{itemize}

\section{Observations}\label{sec:obs}

@@

>>>>

%% Reintroduced the \received and \accepted commands from AASTeX v5.2
%\received{July 1, 2016}
%\revised{September 27, 2016}
%\accepted{\today}
%% Command to document which AAS Journal the manuscript was submitted to.
%% Adds "Submitted to " the arguement.
%\submitjournal{ApJ}

@@

\author{Douglas Kelly}
\affiliation{Steward Observatory \\
933 North Cherry Avenue \\
Tucson, AZ 85721, USA} q

@@

\author{Stephanie Striegel}
\affiliation{Department of Physics \& Astronomy \\
San Jose State University \\
One Washington Square \\
San Jose, CA 95192, USA}
\affiliation{NASA Ames Research Center \\
Space Science and Astrobiology Division \\
Moffett Field, CA 94035, USA}

\author{Xander Levinson}
\affiliation{Department of Astronomy \& Astrophysics \\
University of California, Santa Cruz \\
1156 Highland Street \\
Santa Cruz, CA 95062, USA}
\affiliation{NASA Ames Research Center \\
Space Science and Astrobiology Division \\
Moffett Field, CA 94035, USA}

\author{Thomas P Greene}
\affiliation{NASA Ames Research Center \\
Space Science and Astrobiology Division \\
Moffett Field, CA 94035, USA}

@@

JWST transmission and emission spectra of transiting exoplanets will provide invaluable glimpses at exoplanet atmospheres that reveal the composition and temperature structure at a level never achieved before.
This promising science from JWST, however, will require exquisite precision and understanding of systematic errors that can impact the time series of planets crossing in front of and behind their host stars.
This is especially true if JWST is used to search for biosignatures in temperature atmospheres on Earth-sized planets that may contain liquid water.
Here, we provide the lessons learned from ground-based characterization of the NIRCam H2RG detectors, which will be used for exoplanet spectra and are the same type of detectors used in JWST's NIRISS and NIRSpec instruments.
We summarize the lessons learned from cryogenic vacuum campaigns 2 and 3 at NASA Goddard and the full telescope element at NASA Johnson with the flight hardware, as well as laboratory tests of the same detectors at the University of Arizona's Steward Observatory.

@@

JWST will provide powerful new measurements of exoplanet atmospheres with spectroscopy from 0.6 to 12 $\mu$m
\citep{beichman2014pasp,greene2016jwst_trans,howe2017informationJWST,barstow2015jwstSystematics,schlawin2018JWSTforecasts}.
The sensitivity of JWST combined with its unprecedented wavelength coverage on exoplanets will enable it to measure the abundance of carbon-bearing molecules (CO, CO$2$ and CH$_4$) as well as study cooler, smaller planets than previously characterized.

JWST has also been considered for observations of temperate Earth-like planets that orbit their stars at a distance where where water could be in liquid form on their surface.
The TRAPPIST-1 system \citep{gillon2016trappist1Discovery,gillon2017trappist-1sevenp} presents an exciting opportunity to study Earth-sized stars orbiting a 0.1~R$_\odot$ M-type star.
By putting together 30 transits, it may be possible to collect enough photons to detect CO$_2$ and possibly O$_3$ in the atmosphere of TRAPPIST-1 d with JWST \citep{barstow2016trappist1habitable} if clouds have a minimal impact to its atmosphere.
A critical question in studying a planet like TRAPPIST-1 d, however, is whether photon-limited performance is possible with JWST observations.

@@

The NIRCam instrument \citep{rieke2005NIRCamSPIE} contains a slitless grism mode \citep{greene2017jatisNIRCam} that is analogous to the WFC3 grism mode on HST that has been successfully employed on many transiting planets \citep[e.g.]{deming13,kreidberg2014wasp43,sing2016continuum,wakeford2017hatp26}.
The grism mode will collect moderate resolution R$\sim$1100-1700 spectra and employ the long wavelength channel to cover the wavelength range 2.4 to 5.0~$\mu$m.
This grism mode can be used simultaneously with short wavelength weak lens imaging or the Dispersed Hartmann Sensor mode \citep{schlawin2017dhs}. If it becomes an approved and implemented mode, the DHS will permit spectroscopy from 1.0 to 2.0~$\mu$m and will work for very bright targets inaccessible by other modes.

Section \ref{sec:experiments} describes the experiments on the ground that are used to prepare for JWST observations in flight.

Known detector effects that could affect stability:
\begin{itemize}[noitemsep]
	\item Intrapixel sensitivity - including sub-pixel flat fielding issues, sub-pixel crosshatching on the detectors
	\item Asic-specific effects - pre-amp reset. 
\end{itemize}

The NIRCam detectors

\section{Ground-based Experiments}\label{sec:experiments}

@@

\section{Pre-amp Resets}
The NIRCam detectors' pre-amps are reset once per frame (as opposed to once per integration) to prevent large amplifier drifts over an integration \citep{robberto2014refPixPreAmp}
